---
title: "Stats2 Project2"
output:
  word_document: default
  html_document: default
---

# Load libraries all in one place using pacman package
``` {r}
library(pacman)
p_load("tidyverse", "ggplot2", "caret", "tidyr", "dplyr", "e1071", "class", "gridExtra", "GGally",
       "summarytools", "magrittr")
```

## Load the dataset

You can also embed plots, for example:

```{r}
library(readr)
bank_additional_full <- read.csv("bank-additional-full.csv", sep=";")
dim(bank_additional_full) #count the columns
summary(bank_additional_full)
str(bank_additional_full)
```

```{r}
# Analyzing the data
print(dfSummary(bank_additional_full, graph.magnif = 0.75), method = 'browser')
# "browser" means load the thing in a separate browser instead of embedding it in here, cos its big and it will jsut fill your document
```


Looking at the dfsummary, there doesnt seem to be missing data in terms of just not having values. However, there are some fields that have explicit unknown or non-existent classes that could be considered as 'missing'. For example, loan and housing have 990 "unknown" values. And 'default' has 8597 "unknown" values representing 20.9% 

wondering what is 'pdays' which has a median of 999 but 27 distinct values and appears to be bimodal



```{r}
ggplot(bank_additional_full) + 
  geom_histogram(mapping = aes(x=age, fill=y)) + 
  ggtitle("Distribution of 'y' by age")
```

```{r}
df_yes <- bank_additional_full %>%
  filter(y=="yes")
#summary(df_yes)

# Nothing interesting found in the below code so commenting it out
# ggplot(bank_additional_full, aes(x=age, y=emp.var.rate)) +
#   geom_point(size=1, shape="circle") +
#   ggtitle("Employment Variation Rate vs Age") + 
#   facet_wrap(~ y)

ggplot(bank_additional_full, aes(x=age, y=duration)) +
  geom_point(size=1, shape="circle") + 
  ggtitle("Duration vs Age") + 
  facet_wrap(~ y)

ggplot(bank_additional_full, aes(x=age, y=cons.price.idx)) +
  geom_point(size=1, shape="circle") + 
  ggtitle("Consumer Price Index vs Age")  + 
   facet_wrap(~ y)

# ggplot(bank_additional_full, aes(x=age, y=education)) +
#   geom_point(size=1, shape="circle") + 
#   ggtitle("Education vs Age")  + 
#    facet_wrap(~ y)
```
Duration vs Age: The duration of last contact (in seconds) was longer for ages 25-50. And it was understandably longer for "yes" vs for "no"

```{r}
#Analyzing pdays
ggplot(bank_additional_full) + geom_histogram(mapping = aes(x=pdays, fill=y))
```
- Analyzing 'pdays' ie., number of days that passed by after the client was last contacted from a previous campaign (numeric; 999 means client was not previously contacted)
- Most folks had no previous campaign but if they did, it looks like most who had a previous campaign decided to subscribe

```{r}
#prevly_Cntctd Yes/No. TO see the distribution or 'Y' on first time contact vs. a follow up
bank_additional_full$prevly_Cntctd <- case_when(bank_additional_full$pdays==999 ~ "No", !bank_additional_full$pdays==999 ~ "Yes")

ggplot(bank_additional_full) + 
  geom_bar(mapping = aes(x=prevly_Cntctd, fill = y)) + 
  ggtitle("Number of 'y' by whether customers were prev.contacted or not") +
  ylab("Cnt") + xlab("Previously contacted?")


```
Same observation here as above: Most folks had no previous campaign but if they did, it looks like most who had a previous campaign decided to subscribe / likely to say "Yes"

```{r}
#Analysing campaign
ggplot(bank_additional_full) + 
  geom_histogram(mapping = aes(x=campaign, fill=y)) +
  ggtitle("Distribution of 'y' by campaign")
```
- Just visually, when we decided to stop contacting a person it didnt affect our closing ratio which still dropped off precipitously 

- Ideally, the campaign would stop contacting people who are less likely to subscribe, and keep contacting people if they are more likely to subscribe.  Then we should see the ratio of Yes to No go up as the number of no contacts goes up.  Instead, it looks like the ratio stays the same and the number of Yes's drops proportionately with the number of No's. 

```{r}
#Analyzing job
ggplot(bank_additional_full) + 
  geom_bar(mapping = aes(x=job, fill = y)) + 
  coord_flip() +     #Added coord flip here to make it more readable
  ggtitle("Number of 'y' by job") +
  ylab("Count") + 
  xlab("Job")

```

"y" - has a client subscribed a term deposit? : admin, technician and blue collar jobs are the top 3 subscribers by volume 

```{r}
df <- bank_additional_full %>%
  group_by(job) %>%
  count(y) %>%
  mutate(job_conv = n/sum(n)) %>%
  filter(y == "yes")

ggplot(df, aes(x=job, y=job_conv)) +
  geom_point() +
  coord_flip() +
  facet_wrap(~ y)
```

Above, I looked at the ratio of "yes" vs "no" and see that students and retired persons convert at much higher rates than those of other professions. And 'blue collar' has the lowest conversion rate

So, if they were to want to improve the cost effectiveness of their campaigns they might want to target more 'students' and 'retirees'


```{r}
#Analyzing marital
ggplot(bank_additional_full) + 
  geom_bar(mapping = aes(x=marital, fill = y)) + 
  ggtitle("Number of 'y' by marital") +
  ylab("Cnt") + 
  xlab("marital")

```

- More 'married' people are represented in the campaign
- Visually looking, conversion rate seems to be higher for 'single' people

```{r}
#Analyzing duration

bank_additional_full$duration_group <- 
  cut(bank_additional_full$duration, 
      breaks = c(5,30,60,300,600,Inf), 
      labels = c("5-30s", "30-60s", "1-5 min", "5-10min", "10+"))

df <- bank_additional_full %>%
  group_by(duration_group) %>%
  count(y) %>%
  mutate(duration_group_conv = n/sum(n)) %>%
  filter(y == "yes")

ggplot(df, aes(x=duration_group, y=duration_group_conv)) +
  geom_point() +
  facet_wrap(~ y)
```

- Looking above, clearly conversion rate goes up the longer the most recent call



# HAVING TROUBLE BELOW NEED TO CONTINUE TOMORROW AND FIX IT

# ```{r}
# #Running logistic regression on full data set
# simple.log<-glm (y~.,family="binomial",data=bank_additional_full)
# summary(simple.log)
# 
# ```

# ```{r}
# set.seed(123)
# df <- bank_additional_full %>% drop_na()
# train_idx <- createDataPartition(df$y, p=0.75, list = FALSE)
# train <- bank_additional_full[train_idx, ]
# test <- bank_additional_full[-train_idx, ]
# 
# fit <- train(y ~ ., data = train, 
#              method = "glm", 
#              family = "binomial",
#              trControl = trainControl(method="cv", number = 10))
# summary(fit)
# ```






